---
title: "Aim2 Figures"
author: "Chase Latour"
date: "2025-02-11"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(haven)
library(viridis) 
library(ggstance)

```

# Pull in the Survival Data

```{r }

survival_loss_lt14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_primary_point_1.sas7bdat') %>% 
  mutate(
    Outcome = "Pregnancy Loss",
    GA = "<14 Weeks"
  )

survival_loss_ge14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_primary_point_2.sas7bdat') %>% 
  mutate(
    Outcome = "Pregnancy Loss",
    GA = ">=14 Weeks"
  )

survival_ptb_lt14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_primary_point_ptb_1.sas7bdat') %>% 
  mutate(
    Outcome = "Preterm Birth",
    GA = "<14 Weeks"
  )

survival_ptb_ge14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_primary_point_ptb_2.sas7bdat') %>% 
  mutate(
    Outcome = "Preterm Birth",
    GA = ">=14 Weeks"
  )

## Survival estimates based upon preeclampsia

survival_preec_any_lt14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_preec_any_1.sas7bdat') %>% 
  mutate(
    Outcome = "Preeclampsia (Any Diagnosis)",
    GA = "<14 Weeks"
  )

survival_preec_any_ge14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_preec_any_2.sas7bdat') %>% 
  mutate(
    Outcome = "Preeclampsia (Any Diagnosis)",
    GA = ">=14 Weeks"
  )

survival_preec_inpt_lt14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_preec_inpt_1.sas7bdat') %>% 
  mutate(
    Outcome = "Preeclampsia (Inpatient Diagnosis)",
    GA = "<14 Weeks"
  )

survival_preec_inpt_ge14 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/surv_preec_inpt_2.sas7bdat') %>% 
  mutate(
    Outcome = "Preeclampsia (Inpatient Diagnosis)",
    GA = ">=14 Weeks"
  )



```


# Cumulative Incidence Curves for Study Outcomes

```{r}

# Function to make the plot

cum_incidence_primary <- function(survivaldsn, outcome_quo, ga_quo, ymax=0.35, xmax=260){
  
  ggplot(survivaldsn, aes(x = days, 
                          y = cum_outcome, 
                          color = as.factor(trt), 
                          group = trt)) +
  geom_line(size = 1) +
  geom_point() +  # Optional: Add points for better visualization
  labs(title = paste0("Incidence of ", outcome_quo), 
       subtitle = paste0("Gestational Age ", ga_quo, " at Index"),
       x = "Days from Index Date", 
       y = "Cumualtive Indicidence", color = "Treatment") +
  ylim(0, ymax) + 
  scale_x_continuous(breaks = seq(0, xmax, by = 50),
                     limits = c(0, xmax)) +
  scale_color_manual(values = c("0" = "navy", "1" = "orange"), 
                     labels = c("Labetalol", "Nifedipine")) +
  theme_minimal(base_size = 12)+
  theme(legend.position = c(0.25, 0.8),
        legend.background = element_rect(fill = "white", color = "white"))
  # theme(legend.position = "bottom")
  
  
}


#height and width of figures
h=4
w=4

pdf("Cumulative incidence-loss-lt14 weeks.pdf", height = h, width = w)
cum_incidence_primary(survivalds=survival_loss_lt14,
                      outcome_quo="Pregnancy Loss",
                      ga_quo="<14 Weeks")
dev.off()


pdf("Cumulative incidence-loss-ge14 weeks.pdf", height=h, width=w)
cum_incidence_primary(survivalds=survival_loss_ge14,
                      outcome_quo="Pregnancy Loss",
                      ga_quo=">=14 Weeks")
dev.off()

pdf("Cumulative incidence-ptb-lt14 weeks.pdf", height=h, width=w)
cum_incidence_primary(survivalds=survival_ptb_lt14,
                      outcome_quo="Preterm Birth",
                      ga_quo="<14 Weeks")
dev.off()

pdf("Cumulative incidence-ptb-ge14 weeks.pdf", height=h, width=w)
cum_incidence_primary(survivalds=survival_ptb_ge14,
                      outcome_quo="Preterm Birth",
                      ga_quo=">=14 Weeks")
dev.off()


# Preeclampsia outcomes


pdf("Cumulative incidence-preeclampsia any-lt14 weeks.pdf", height = h, width = w)
cum_incidence_primary(survivalds=survival_preec_any_lt14,
                      outcome_quo="Preeclampsia (Any Diagnosis)",
                      ga_quo="<14 Weeks",
                      ymax = 0.4, xmax=274)
dev.off()


pdf("Cumulative incidence-preeclampsia any-ge14 weeks.pdf", height = h, width = w)
cum_incidence_primary(survivalds=survival_preec_any_ge14,
                      outcome_quo="Preeclampsia (Any Diagnosis)",
                      ga_quo=">=14 Weeks",
                      ymax = 0.4, xmax=274)
dev.off()


pdf("Cumulative incidence-preeclampsia inpt-lt14 weeks.pdf", height = h, width = w)
cum_incidence_primary(survivalds=survival_preec_inpt_lt14,
                      outcome_quo="Preeclampsia (Inpatient Diagnosis)",
                      ga_quo="<14 Weeks",
                      ymax = 0.4, xmax=274)
dev.off()


pdf("Cumulative incidence-preeclampsia inpt-ge14 weeks.pdf", height = h, width = w)
cum_incidence_primary(survivalds=survival_preec_inpt_ge14,
                      outcome_quo="Preeclampsia (Inpatient Diagnosis)",
                      ga_quo=">=14 Weeks",
                      ymax = 0.4, xmax=274)
dev.off()



```

# Pull in the Cohort Data

```{r}

trim_cohort_lt14 <-  read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_cohort_trim_1.sas7bdat')

trim_cohort_ge14 <-  read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_cohort_trim_2.sas7bdat')

# Get the cohorts with information on preeclampsia outcome date
trim_cohort_lt14_pre <-  read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preeclampsia_any_trim_1.sas7bdat')

trim_cohort_ge14_pre <-  read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preeclampsia_any_trim_2.sas7bdat')


#FUNCTION: get_loss_counts
# Get the relevant counts of number of people at-risk for pregnancy loss outcome
get_loss_counts <- function(dsn){
  
  # Get counts for Loss
  dsn %>% 
    mutate(
      p250 = ifelse(dt_gapreg - dt_index >= 250, 1, 0),
      p200 = ifelse(dt_gapreg - dt_index >= 200, 1, 0),
      p150 = ifelse(dt_gapreg - dt_index >= 150, 1, 0),
      p100 = ifelse(dt_gapreg - dt_index >= 100, 1, 0),
      p50 = ifelse(dt_gapreg - dt_index >= 50, 1, 0),
      p0 = ifelse(dt_gapreg - dt_index >= 0, 1, 0)
    ) %>% 
    group_by(trt) %>% 
    summarize(
      sum0 = sum(p0),
      sum50 = sum(p50),
      sum100 = sum(p100),
      sum150 = sum(p150),
      sum200 = sum(p200),
      sum250 = sum(p250)
    )
  
}


get_ptb_counts <- function(dsn){
  
  dsn %>% 
    mutate(
      p250 = ifelse(dt_gapreg_ptb - dt_index >= 250, 1, 0),
      p200 = ifelse(dt_gapreg_ptb - dt_index >= 200, 1, 0),
      p150 = ifelse(dt_gapreg_ptb - dt_index >= 150, 1, 0),
      p100 = ifelse(dt_gapreg_ptb - dt_index >= 100, 1, 0),
      p50 = ifelse(dt_gapreg_ptb - dt_index >= 50, 1, 0),
      p0 = ifelse(dt_gapreg_ptb - dt_index >= 0, 1, 0)
    ) %>% 
    group_by(trt) %>% 
    summarize(
      sum0 = sum(p0),
      sum50 = sum(p50),
      sum100 = sum(p100),
      sum150 = sum(p150),
      sum200 = sum(p200),
      sum250 = sum(p250)
    )
  
}

get_preec_counts <- function(dsn){
  
  dsn %>% 
    mutate(
      p250 = ifelse(preec_any_dt - dt_index >= 250, 1, 0),
      p200 = ifelse(preec_any_dt - dt_index >= 200, 1, 0),
      p150 = ifelse(preec_any_dt - dt_index >= 150, 1, 0),
      p100 = ifelse(preec_any_dt - dt_index >= 100, 1, 0),
      p50 = ifelse(preec_any_dt - dt_index >= 50, 1, 0),
      p0 = ifelse(preec_any_dt - dt_index >= 0, 1, 0)
    ) %>% 
    group_by(trt) %>% 
    summarize(
      sum0 = sum(p0),
      sum50 = sum(p50),
      sum100 = sum(p100),
      sum150 = sum(p150),
      sum200 = sum(p200),
      sum250 = sum(p250)
    )
  
}


# Get loss counts
get_loss_counts(trim_cohort_lt14)
get_loss_counts(trim_cohort_ge14)

# Get ptb counts
get_ptb_counts(trim_cohort_lt14)
get_ptb_counts(trim_cohort_ge14)

# Get preeclampsia counts (any diagnosis code)
get_preec_counts(trim_cohort_lt14_pre)
get_preec_counts(trim_cohort_ge14_pre)




```


# Cumulative Incidence Curves for Pregnancy Outcomes

```{r}

# Function to make the plot

cum_incidence_primary <- function(survivaldsn, ga_quo, trt_quo){
  
  dsn <- survivaldsn %>% 
     mutate(
        IAB = cum_comprisk1,
        SAB = cum_comprisk1+cum_outcome,
        LB = cum_comprisk1+cum_outcome+cum_comprisk2
      ) %>% 
    select(trt, days, IAB, SAB, LB) %>% 
    pivot_longer(
      cols = c(IAB, SAB, LB),
      names_to = "Outcome",
      values_to = "Incidence"
    ) %>% 
    mutate(
      Outcome = case_when(Outcome == 'IAB' ~ "Induced Abortion",
                          Outcome == "SAB" ~ "Pregnancy Loss",
                          Outcome == "LB" ~ "Live Birth")
    )
  
  plot <- ggplot(dsn, aes(x = days,
                  y = Incidence, 
                  color = as.factor(Outcome), 
                  group = Outcome)) +
  geom_line(size = 1) +
  # geom_point() +  # Optional: Add points for better visualization
  labs(title = paste0("Gestational Age ", ga_quo, " at Index"), 
       subtitle = paste0(trt_quo, " Initiators"),
       x = "Days from Index Date", 
       y = "Cumualtive Indicidence", 
       color = "Outcome") +
  ylim(0, 1.01) + 
  scale_x_continuous(breaks = seq(0, 260, by = 50),
                     limits = c(0, 260)) +
  scale_color_manual(values = c("Induced Abortion" = "#009E73", 
                                "Pregnancy Loss" = "#0072B2", 
                                "Live Birth" = "#D55E00")) +#,
                     # labels = c("IAB"="Induced Abortion",
                     #            "SAB" = "Pregnancy Loss",
                     #            "LB" = "Live birth")) +
  theme_minimal(base_size = 11)+
  theme(legend.position = "bottom")
  
  return(plot)
  
}







#height and width of figures
h=5
w=5

pdf("Cumulative incidence-all-lt14 weeks-trt0.pdf", height = h, width = w)
cum_incidence_primary(survivalds=subset(survival_loss_lt14, trt==0),
                      ga_quo="<14 Weeks",
                      trt_quo="Labetalol")
dev.off()


pdf("Cumulative incidence-all-ge14 weeks-trt0.pdf", height=h, width=w)
cum_incidence_primary(survivalds=subset(survival_loss_ge14, trt==0),
                      ga_quo=">=14 Weeks",
                      trt_quo="Labetalol")
dev.off()

pdf("Cumulative incidence-all-lt14 weeks-trt1.pdf", height=h, width=w)
cum_incidence_primary(survivalds=subset(survival_loss_lt14, trt==1),
                      ga_quo="<14 Weeks",
                      trt_quo="Nifedipine")
dev.off()

pdf("Cumulative incidence-all-ge14 weeks-trt1.pdf", height=h, width=w)
cum_incidence_primary(survivalds=subset(survival_loss_ge14, trt==1),
                      ga_quo=">=14 Weeks",
                      trt_quo="Nifedipine")
dev.off()





```



# Plot the sensitivity analyses for missingness

### Function to pull together bounds data

```{r}

bounds_data <- function(outc_quo='loss', bound_quo='partialb'){
  
  # Point Estimates

  both_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_' , 'both_', outc_quo, '_point_all.sas7bdat')) %>% 
    mutate(assumption = "Both")

  none_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_' , 'none_', outc_quo, '_point_all.sas7bdat')) %>% 
    mutate(assumption = "None")

  nif_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_' , 'nif_', outc_quo, '_point_all.sas7bdat')) %>% 
    mutate(assumption = "Nifedipine")
  
  lab_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_' , 'lab_', outc_quo, '_point_all.sas7bdat')) %>% 
    mutate(assumption = "Labetalol")
  
  est <- rbind(both_est, none_est) %>% 
    rbind(nif_est) %>% 
    rbind(lab_est)
  
  # Standard errors from bootstrap
  
  both_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_both_', outc_quo,'_boot_all.sas7bdat')) %>%   
    mutate(assumption = "Both")
  
  none_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_none_', outc_quo,'_boot_all.sas7bdat')) %>%   
    mutate(assumption = "None")
  
  nif_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_nif_', outc_quo,'_boot_all.sas7bdat')) %>%   
    mutate(assumption = "Nifedipine")
  
  lab_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_lab_', outc_quo,'_boot_all.sas7bdat')) %>%   
    mutate(assumption = "Labetalol")
  
  se <- rbind(both_se, none_se) %>% 
    rbind(nif_se) %>% 
    rbind(lab_se) %>% 
    select(c(estimate, stderr, assumption)) %>% 
    filter(estimate == 'rd' | estimate == 'rr') %>% 
    pivot_wider(names_from = estimate, 
                values_from = stderr, 
                names_prefix = "se_")
  
  # Now, join them all together
  
  all <- left_join(est, se, by="assumption") 
  
  return(all)
  
}



### Function to get partial bounds for loss -- Datasets were named differently from the others.

pbounds_loss_data <- function(bound_quo='partialb'){
  
  # Point Estimates

  both_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_overall_both.sas7bdat')) %>% 
    mutate(assumption = "Both")

  none_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_overall_none.sas7bdat')) %>% 
    mutate(assumption = "None")

  nif_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_overall_nif.sas7bdat')) %>% 
    mutate(assumption = "Nifedipine")
  
  lab_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_overall_lab.sas7bdat')) %>% 
    mutate(assumption = "Labetalol")
  
  est <- rbind(both_est, none_est) %>% 
    rbind(nif_est) %>% 
    rbind(lab_est)
  
  # Standard errors from bootstrap
  
  both_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_overall_both.sas7bdat')) %>%   
    mutate(assumption = "Both")
  
  none_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_overall_none.sas7bdat')) %>%   
    mutate(assumption = "None")
  
  nif_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_overall_nif.sas7bdat')) %>%   
    mutate(assumption = "Nifedipine")
  
  lab_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_overall_lab.sas7bdat')) %>%   
    mutate(assumption = "Labetalol")
  
  se <- rbind(both_se, none_se) %>% 
    rbind(nif_se) %>% 
    rbind(lab_se) %>% 
    select(c(estimate, stderr, assumption)) %>% 
    filter(estimate == 'rd' | estimate == 'rr') %>% 
    pivot_wider(names_from = estimate, 
                values_from = stderr, 
                names_prefix = "se_")
  
  # Now, join them all together
  
  all <- left_join(est, se, by="assumption") 
  
  return(all)
  
}




### Function to get partial bounds for ptb -- Datasets were named differently from the others.

pbounds_ptb_data <- function(bound_quo='partialb', outcome_quo='ptb'){
  
  # Point Estimates

  both_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_', outcome_quo,'_overall_both.sas7bdat')) %>% 
    mutate(assumption = "Both")

  none_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_', outcome_quo,'_overall_none.sas7bdat')) %>% 
    mutate(assumption = "None")

  nif_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_', outcome_quo,'_overall_nif.sas7bdat')) %>% 
    mutate(assumption = "Nifedipine")
  
  lab_est <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo, '_point_', outcome_quo,'_overall_lab.sas7bdat')) %>% 
    mutate(assumption = "Labetalol")
  
  est <- rbind(both_est, none_est) %>% 
    rbind(nif_est) %>% 
    rbind(lab_est)
  
  # Standard errors from bootstrap
  
  both_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_', outcome_quo,'_overall_both.sas7bdat')) %>%   
    mutate(assumption = "Both")
  
  none_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_', outcome_quo,'_overall_none.sas7bdat')) %>%   
    mutate(assumption = "None")
  
  nif_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_', outcome_quo,'_overall_nif.sas7bdat')) %>%   
    mutate(assumption = "Nifedipine")
  
  lab_se <- read_sas(paste0('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/',bound_quo,'_boot_', outcome_quo,'_overall_lab.sas7bdat')) %>%   
    mutate(assumption = "Labetalol")
  
  se <- rbind(both_se, none_se) %>% 
    rbind(nif_se) %>% 
    rbind(lab_se) %>% 
    select(c(estimate, stderr, assumption)) %>% 
    filter(estimate == 'rd' | estimate == 'rr') %>% 
    pivot_wider(names_from = estimate, 
                values_from = stderr, 
                names_prefix = "se_")
  
  # Now, join them all together
  
  all <- left_join(est, se, by="assumption") 
  
  return(all)
  
}



```

## Function to Make Plots

```{r}


make_plot <- function(point_est, full_bounds, partial_bounds, outcome_quo){
  
  # Get the qnorm value for 95% confidence intervals
  z <- qnorm(0.975, 0, 1)
  
  point_all <- point_est %>% 
    mutate(
      analysis = "Primary",
      sens = "Primary",
    )
  
  # Make a differential and non-differential version
  full_bounds <- full_bounds %>% 
    mutate(
      sens = ifelse(assumption == "Both" | assumption == "None",
                    "Non-Differential",
                    "Differential")
    )
  
  partial_bounds <- partial_bounds %>% 
    mutate(
      sens = ifelse(assumption == "Both" | assumption == "None",
                    "Non-Differential",
                    "Differential")
    )

  # Derive the confidence intervals for the effect estimates
  estimates <- rbind(point_all, full_bounds) %>% 
    rbind(partial_bounds) %>% 
    mutate(
      rd_lcl = 100*(rd - (z*se_rd)),
      rd_ucl = 100*(rd + (z*se_rd)),
      rd = 100*rd,
      rr_lcl = exp(log(rr) - (z*se_rr)),
      rr_ucl = exp(log(rr) + (z*se_rr)),
      assumption = ifelse(assumption == "None", "Neither", assumption)
    )
  
  # Make analysis a factor variable so that it prints in the desired order
  estimates$sens <- factor(estimates$sens,
                           levels = c("Non-Differential", "Differential", "Primary"))
  
  estimates$assumption <- factor(estimates$assumption,
                                 levels = c("Both", "Neither","Nifedipine", "Labetalol", "Primary"))
  
  estimates <- estimates %>% 
    arrange(analysis, sens, assumption)

  # Risk Difference Plot

  rd <- ggplot(estimates, aes(x = rd, y = analysis, color=sens, shape=assumption))+
    geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
    geom_errorbar(aes(xmin = rd_lcl, xmax = rd_ucl),
                  position = ggstance::position_dodgev(height = 0.5),
                  width = 0)+
    labs(
        title = paste0(outcome_quo),
        x = "Risk Difference (per 100)",  # Label for x-axis
        y = NULL,  # Label for y-axis
        color = "Censoring Across\nTreatment",
        shape = "Treatment Group\nAssumed to\nExperience\nthe Outcome"
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
    theme_minimal() +
    scale_color_manual(
      values = c("Non-Differential" = "#D55E00",
                 "Differential" = "#0072B2",
                 "Primary" = "black"),
      labels = c("Non-Differential", "Differential", "Primary")
    ) +
    scale_shape_manual(
      values = c("Nifedipine"=15, "Labetalol"=17,"Both"=7, "Neither"=3,"Primary"=16)
    ) +
    scale_x_continuous(limits = c(-15, 25)) +
    theme(
      axis.text.y = element_text(color = "black", 
                                 #face = "bold", 
                                 angle = 90, 
                                 vjust = 0.5, hjust = 0.5),
      axis.ticks.y = element_blank()
    )
  
  
  
  rr <- ggplot(estimates, aes(x = rr, y = analysis, color=sens, shape=assumption))+
    geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
    geom_errorbar(aes(xmin = rr_lcl, xmax = rr_ucl),
                  position = ggstance::position_dodgev(height = 0.5),
                  width = 0)+
    scale_x_continuous(trans = "log10", limits = c(0.2, 7)) +
    labs(
        title = paste0(outcome_quo),
        x = "Risk Ratio (Log-Scaled)",  # Label for x-axis
        y = NULL,  # Label for y-axis
        color = "Censoring Across\nTreatment",
        shape = "Treatment Group\nAssumed to\nExperience\nthe Outcome"
    ) +
    geom_vline(xintercept = 1, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
    theme_minimal() +
    scale_color_manual(
      values = c("Non-Differential" = "#D55E00",
                 "Differential" = "#0072B2",
                 "Primary" = "black"),
      labels = c("Non-Differential", "Differential", "Primary")
    ) +
    scale_shape_manual(
      values = c("Nifedipine"=15, "Labetalol"=17,"Both"=7, "Neither"=3,"Primary"=16)
    ) +
    theme(
      axis.text.y = element_text(color = "black", 
                                 #face = "bold", 
                                 angle = 90, 
                                 vjust = 0.5, hjust = 0.5),
      axis.ticks.y = element_blank()
    )


  return(list(
    rd = rd,
    rr = rr
  ))
  
  
}







make_plot2 <- function(point_est, full_bounds, partial_bounds, outcome_quo){
  
  # Get the qnorm value for 95% confidence intervals
  z <- qnorm(0.975, 0, 1)
  
  point_all <- point_est %>% 
    mutate(
      analysis = "Primary",
      sens = "Primary",
    )
  
  # Make a differential and non-differential version
  full_bounds <- full_bounds %>% 
    mutate(
      sens = ifelse(assumption == "Both" | assumption == "None",
                    "Non-Differential",
                    "Differential")
    )
  
  partial_bounds <- partial_bounds %>% 
    mutate(
      sens = ifelse(assumption == "Both" | assumption == "None",
                    "Non-Differential",
                    "Differential")
    )

  # Derive the confidence intervals for the effect estimates
  estimates <- rbind(point_all, full_bounds) %>% 
    rbind(partial_bounds) %>% 
    mutate(
      rd_lcl = 100*(rd - (z*se_rd)),
      rd_ucl = 100*(rd + (z*se_rd)),
      rd = 100*rd,
      rr_lcl = exp(log(rr) - (z*se_rr)),
      rr_ucl = exp(log(rr) + (z*se_rr)),
      assumption = ifelse(assumption == "None", "Neither", assumption)
    )
  
  # Make analysis a factor variable so that it prints in the desired order
  estimates$sens <- factor(estimates$sens,
                           levels = c("Non-Differential", "Differential", "Primary"))
  
  estimates$assumption <- factor(estimates$assumption,
                                 levels = c("Both", "Neither","Nifedipine", "Labetalol", "Primary"))
  
  estimates <- estimates %>% 
    arrange(analysis, sens, assumption)
  
  # Create a combined variable in estimates
  estimates$legend_group <- paste(estimates$sens, 
                                  estimates$assumption, 
                                  sep = " - ")


  # Risk Difference Plot

  rd <- ggplot(estimates, aes(x = rd, y = analysis, color=assumption, shape=assumption))+
    geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
    geom_errorbar(aes(xmin = rd_lcl, xmax = rd_ucl),
                  position = ggstance::position_dodgev(height = 0.5),
                  width = 0)+
    labs(
        title = paste0(outcome_quo),
        x = "Risk Difference (per 100)",  # Label for x-axis
        y = NULL,  # Label for y-axis
        color = "Treatment Group\nAssumed to\nExperience\nthe Outcome",
        shape = "Treatment Group\nAssumed to\nExperience\nthe Outcome"
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
    theme_minimal() +
    scale_color_manual(
      values = c(
        "Both" = "#D55E00",
        "Neither" = "#D55E00",
        "Nifedipine" = "#0072B2",
        "Labetalol" = "#0072B2",
        "Primary" = "black"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Both" = 7,
        "Neither" = 3,
        "Nifedipine" = 15,
        "Labetalol" = 17,
        "Primary" = 16
      )
    ) +
    scale_x_continuous(limits = c(-15, 25)) +
    theme(
      axis.text.y = element_text(color = "black", 
                                 #face = "bold", 
                                 angle = 90, 
                                 vjust = 0.5, hjust = 0.5),
      axis.ticks.y = element_blank()
    )
  
  
  
  rr <- ggplot(estimates, aes(x = rr, y = analysis, color=assumption, shape=assumption))+
    geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
    geom_errorbar(aes(xmin = rr_lcl, xmax = rr_ucl),
                  position = ggstance::position_dodgev(height = 0.5),
                  width = 0)+
    scale_x_continuous(trans = "log10", limits = c(0.2, 7)) +
    labs(
        title = paste0(outcome_quo),
        x = "Risk Ratio (Log-Scaled)",  # Label for x-axis
        y = NULL,  # Label for y-axis
        color = "Treatment Group\nAssumed to\nExperience\nthe Outcome",
        shape = "Treatment Group\nAssumed to\nExperience\nthe Outcome"
    ) +
    geom_vline(xintercept = 1, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
    theme_minimal() +
    scale_color_manual(
      values = c(
        "Both" = "#D55E00",
        "Neither" = "#D55E00",
        "Nifedipine" = "#0072B2",
        "Labetalol" = "#0072B2",
        "Primary" = "black"
      )
    ) +
    scale_shape_manual(
      values = c(
        "Both" = 7,
        "Neither" = 3,
        "Nifedipine" = 15,
        "Labetalol" = 17,
        "Primary" = 16
      )
    ) +
    theme(
      axis.text.y = element_text(color = "black", 
                                 #face = "bold", 
                                 angle = 90, 
                                 vjust = 0.5, hjust = 0.5),
      axis.ticks.y = element_blank()
    )


  return(list(
    rd = rd,
    rr = rr
  ))
  
  
}

# make_plot <- function(point_est, full_bounds, partial_bounds, outcome_quo){
#   
#   # Get the qnorm value for 95% confidence intervals
#   z <- qnorm(0.975, 0, 1)
#   
#   point_est_full <- point_est %>% 
#     mutate(
#       analysis = "Full Bounds",
#       sens = "Primary"
#     )
#   
#   point_est_partial <- point_est %>% 
#     mutate(
#       analysis = "Enrollment Bounds",
#       sens = "Primary"
#     )
#   
#   point_all <- rbind(point_est_full, point_est_partial)
#   
#   full_bounds$sens <- "Sensitivity"
#   partial_bounds$sens <- "Sensitivity"
#   
#   # Derive the confidence intervals for the effect estimates
#   estimates <- rbind(point_all, full_bounds) %>% 
#     rbind(partial_bounds) %>% 
#     mutate(
#       rd_lcl = 100*(rd - (z*se_rd)),
#       rd_ucl = 100*(rd + (z*se_rd)),
#       rd = 100*rd,
#       rr_lcl = exp(log(rr) - (z*se_rr)),
#       rr_ucl = exp(log(rr) + (z*se_rr))
#     )
#   
#   # # Make analysis a factor variable so that it prints in the desired order
#   # estimates$analysis <- factor(estimates$analysis, 
#   #                              levels = c("Primary", "Partial Bounds", "Full Bounds"))
#   
#   # Risk Difference Plot
# 
#   rd <- ggplot(estimates, aes(x = rd, y = analysis, color=sens, shape=sens, group = assumption))+
#     geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
#     geom_errorbar(aes(xmin = rd_lcl, xmax = rd_ucl),
#                   position = ggstance::position_dodgev(height = 0.5),
#                   width = 0)+
#     theme(legend.position = "bottom") +
#     labs(
#         title = "Risk Differences", 
#         subtitle = paste0(outcome_quo),
#         x = "Risk Difference",  # Label for x-axis
#         y = "Sensitivity Analysis",  # Label for y-axis
#         color = "Analysis",
#         shape = "Analysis"
#     ) +
#     geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
#     # Labels with horizontal alignment shift
#     geom_text(aes(label = ifelse(assumption == "Primary", '', assumption)), 
#               size = 2.5, 
#               color = "black",
#               position = ggstance::position_dodgev(height = 0.5),
#               vjust = 1.7
#               ) +
#     theme_minimal() +
#     scale_x_continuous(limits = c(-15, 25)) +
#     theme(axis.text.y = element_text(angle = 45, hjust = 1, vjust = -1.5))
#   
#   
#   rr <- ggplot(estimates, aes(x = rr, y = analysis, color=sens, shape=sens, group = assumption))+
#     geom_point(size=2, position = ggstance::position_dodgev(height = 0.5)) + 
#     geom_errorbar(aes(xmin = rr_lcl, xmax = rr_ucl),
#                   position = ggstance::position_dodgev(height = 0.5),
#                   width = 0)+
#     scale_x_continuous(trans = "log10", limits = c(0.2, 7)) +
#     theme(legend.position = "bottom") +
#     labs(
#         title = "Risk Ratios", 
#         subtitle = paste0(outcome_quo),
#         x = "Risk Ratio",  # Label for x-axis
#         y = "Sensitivity Analysis",  # Label for y-axis
#         color = "Analysis",
#         shape = "Analysis"
#     ) +
#     geom_vline(xintercept = 1, linetype = "dashed", linewidth = 0.8, color = "darkgrey") +
#     # Labels with horizontal alignment shift
#     geom_text(aes(label = ifelse(assumption == "Primary", '', assumption)), 
#               size = 2.5, 
#               color = "black",
#               position = ggstance::position_dodgev(height = 0.5),
#               vjust = 1.7
#               ) +
#     theme_minimal() +
#     theme(axis.text.y = element_text(angle = 45, hjust = 1, vjust = -1.5))
# 
# 
#   return(list(
#     rd = rd,
#     rr = rr
#   ))
#   
#   
# }


```

## Pregnancy Loss

```{r}

# point Estimate

primary_loss <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_overall.sas7bdat')

# SE via bootstrap

primary_loss_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_")

# now join these together

loss <- cbind(primary_loss, primary_loss_se) %>% 
  mutate(
    assumption = "Primary",
    analysis = "Primary"
  )

## Get data for full Bounds

full_loss <- bounds_data(outc_quo='loss',bound_quo='fullbounds') %>% 
  mutate(analysis = "Full Bounds")

## Get data for partial bounds

partial_loss <- pbounds_loss_data(bound_quo='partialb') %>% 
  mutate(analysis = "Enrollment Bounds")

# Make the figures

loss_figures <- make_plot(point_est = loss, 
                          full_bounds = full_loss, 
                          partial_bounds = partial_loss, 
                          outcome_quo = "Pregancy Loss")

# Now print and save the figures as PDFs

h <- 4.5
w <- 4.5

pdf("RDs_bounds_loss.pdf", height=h, width=w)
loss_figures[[1]]
dev.off()

pdf("RRs_bounds_loss.pdf", height=h, width=w)
loss_figures[[2]]
dev.off()





loss_figures2 <- make_plot2(point_est = loss, 
                          full_bounds = full_loss, 
                          partial_bounds = partial_loss, 
                          outcome_quo = "Pregancy Loss")

# Now print and save the figures as PDFs

h <- 4.5
w <- 4.5

pdf("RDs_bounds_loss2.pdf", height=h, width=w)
loss_figures2[[1]]
dev.off()

pdf("RRs_bounds_loss2.pdf", height=h, width=w)
loss_figures2[[2]]
dev.off()

```

## Preterm Birth

```{r}

# point Estimate

primary_ptb <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_ptb_overall.sas7bdat')

# SE viai bootstrap

primary_ptb_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_ptb_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_")

# now join these together

ptb <- cbind(primary_ptb, primary_ptb_se) %>% 
  mutate(
    assumption = "Primary",
    analysis = "Primary"
  )

## Get data for full Bounds

full_ptb <- bounds_data(outc_quo='ptb',bound_quo='fullbounds') %>% 
  mutate(analysis = "Full Bounds")

## Get data for partial bounds

partial_ptb <- pbounds_ptb_data(bound_quo='partialb') %>% 
  mutate(analysis = "Enrollment Bounds")

# Make the figures

ptb_figures2 <- make_plot2(point_est = ptb, 
                         full_bounds = full_ptb, 
                         partial_bounds = partial_ptb, 
                         outcome_quo = "Preterm Birth")

# Now print and save the figures as PDFs

h <- 4.5
w <- 4.5


pdf("RDs_bounds_ptb2.pdf", height=h, width=w)
ptb_figures2[[1]]
dev.off()

pdf("RRs_bounds_ptb2.pdf", height=h, width=w)
ptb_figures2[[2]]
dev.off()




# Make second set of figures with combined legend

```




## Preeclampsia (Any Location)

```{r}

# point Estimate

primary_preec <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_point_overall.sas7bdat')

# SE viai bootstrap

primary_preec_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_")

# now join these together

preec <- cbind(primary_preec, primary_preec_se) %>% 
  mutate(
    assumption = "Primary",
    analysis = "Primary"
  )

## Get data for full Bounds

full_preec <- bounds_data(outc_quo='pany',bound_quo='fullbounds') %>% 
  mutate(analysis = "Full Bounds")

## Get data for partial bounds

partial_preec <- pbounds_ptb_data(bound_quo='partialb', outcome_quo = 'pany') %>% 
  mutate(analysis = "Enrollment Bounds")

# Make the figures

preec_figures2 <- make_plot2(point_est = preec, 
                         full_bounds = full_preec, 
                         partial_bounds = partial_preec, 
                         outcome_quo = "Preeclampsia")

# Now print and save the figures as PDFs

h <- 4.5
w <- 4.5


pdf("RDs_bounds_preec2.pdf", height=h, width=w)
#jpeg("RDs_bounds_preec2.jpg", height=h, width=w, units="in", res=300)
preec_figures2[[1]]
dev.off()

pdf("RRs_bounds_preec2.pdf", height=h, width=w)
#jpeg("RRs_bounds_preec2.jpg", height=h, width=w,  units="in", res=300)
preec_figures2[[2]]
dev.off()




# Make second set of figures with combined legend

```


# Figures For risks, RDs, and RRs combined

## Pull in the necessary data

```{r}

# Pregnancy Loss

### point Estimate
primary_loss <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_overall.sas7bdat') %>% 
  mutate(strata = 0,
         outcome = "loss")
loss1 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_1.sas7bdat') %>% 
  mutate(strata = 1,
         outcome = "loss")
loss2 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_2.sas7bdat') %>% 
  mutate(strata = 2,
         outcome = "loss")
strata_loss <- rbind(loss1, loss2) %>% 
  rename(
    risk0 = e0_risk,
    risk1 = e1_risk,
    rd = riskDiff,
    rr = riskRatio
  ) %>% 
  select(risk0, risk1, rd, rr, strata, outcome)

### SE via bootstrap
primary_loss_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(strata = 0,
         outcome = "loss")
strata_loss_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_boot_strat.sas7bdat') %>% 
  select(estimate, stderr, strata) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(id_cols = strata,
              names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(outcome = "loss")


## Now combine these all together

point <- left_join(primary_loss, primary_loss_se, by = c("strata","outcome"))
strata <- left_join(strata_loss, strata_loss_se, by = c("strata","outcome"))
loss <- rbind(point, strata)




# Preterm Birth

### point Estimate
primary_ptb <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_ptb_overall.sas7bdat') %>% 
  mutate(strata = 0,
         outcome = "ptb")
ptb1 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_ptb_1.sas7bdat') %>% 
  mutate(strata = 1,
         outcome = "ptb")
ptb2 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_point_ptb_2.sas7bdat') %>% 
  mutate(strata = 2,
         outcome = "ptb")
strata_ptb <- rbind(ptb1, ptb2) %>% 
  rename(
    risk0 = e0_risk,
    risk1 = e1_risk,
    rd = riskDiff,
    rr = riskRatio
  ) %>% 
  select(risk0, risk1, rd, rr, strata, outcome)

### SE via bootstrap
primary_ptb_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_ptb_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(strata = 0,
         outcome = "ptb")
strata_ptb_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/primary_ptb_boot_strat.sas7bdat') %>% 
  select(estimate, stderr, strata) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(id_cols = strata,
              names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(outcome = "ptb")


## Now combine these all together

point <- left_join(primary_ptb, primary_ptb_se, by = c("strata","outcome"))
strata <- left_join(strata_ptb, strata_ptb_se, by = c("strata","outcome"))
ptb <- rbind(point, strata)








# Preeclampsia (Any service location)

### point Estimate
primary_preec <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_point_overall.sas7bdat') %>% 
  mutate(strata = 0,
         outcome = "preec")
preec1 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_point_1.sas7bdat') %>% 
  mutate(strata = 1,
         outcome = "preec")
preec2 <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_point_2.sas7bdat') %>% 
  mutate(strata = 2,
         outcome = "preec")
strata_preec <- rbind(preec1, preec2) %>% 
  rename(
    risk0 = e0_risk,
    risk1 = e1_risk,
    rd = riskDiff,
    rr = riskRatio
  ) %>% 
  select(risk0, risk1, rd, rr, strata, outcome)

### SE via bootstrap
primary_preec_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(strata = 0,
         outcome = "preec")
strata_preec_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_any_boot_strat.sas7bdat') %>% 
  select(estimate, stderr, strata) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(id_cols = strata,
              names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(outcome = "preec")


## Now combine these all together

point <- left_join(primary_preec, primary_preec_se, by = c("strata","outcome"))
strata <- left_join(strata_preec, strata_preec_se, by = c("strata","outcome"))
preec <- rbind(point, strata)








# Preeclampsia (Inpatient)

### point Estimate
primary_preec_inpt <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_inpt_point_overall.sas7bdat') %>% 
  mutate(strata = 0,
         outcome = "preec_inpt")
preec1_inpt <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_inpt_point_1.sas7bdat') %>% 
  mutate(strata = 1,
         outcome = "preec_inpt")
preec2_inpt <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_inpt_point_2.sas7bdat') %>% 
  mutate(strata = 2,
         outcome = "preec_inpt")
strata_preec_inpt <- rbind(preec1_inpt, preec2_inpt) %>% 
  rename(
    risk0 = e0_risk,
    risk1 = e1_risk,
    rd = riskDiff,
    rr = riskRatio
  ) %>% 
  select(risk0, risk1, rd, rr, strata, outcome)

### SE via bootstrap
primary_preec_inpt_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_inpt_boot_overall.sas7bdat') %>% 
  select(estimate, stderr) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(strata = 0,
         outcome = "preec_inpt")
strata_preec_inpt_se <- read_sas('/local/projects/marketscan_preg/Latour_23_2322/data/full/analysis/preec_inpt_boot_strat.sas7bdat') %>% 
  select(estimate, stderr, strata) %>% 
  filter(estimate == 'rd' | estimate == 'rr') %>% 
  pivot_wider(id_cols = strata,
              names_from = estimate, 
              values_from = stderr, 
              names_prefix = "se_") %>% 
  mutate(outcome = "preec_inpt")


## Now combine these all together

point <- left_join(primary_preec_inpt, primary_preec_inpt_se, by = c("strata","outcome"))
strata <- left_join(strata_preec_inpt, strata_preec_inpt_se, by = c("strata","outcome"))
preec_inpt <- rbind(point, strata)




# Now stack all of the datasets together
point_estimates <- rbind(loss, ptb) %>% 
  rbind(preec) %>% 
  rbind(preec_inpt)

```

```{r}

# For now, subset to just the overall estimates
point_estimates_overall <- point_estimates %>% 
  filter(strata == 0)

point_estimates_overall$outcome <- factor(
  point_estimates_overall$outcome,
  levels = c("preec_inpt", "preec", "ptb", "loss"),
  labels = c("Preeclampsia (Inpatient)",
             "Preeclampsia (Any Location)",
             "Preterm Birth",
             "Pregnancy Loss")
)

## Calculate the confidence intervals

z <- qnorm(0.975)

point_estimates_overall <- point_estimates_overall %>% 
  mutate(
    rd_lcl = rd - (z*se_rd),
    rd_ucl = rd + (z*se_rd),
    rr_lcl = exp(log(rr) - (z*se_rr)),
    rr_ucl = exp(log(rr) + (z*se_rr)),
  )


h <- 4.5
w <- 4.5

## Print the Risks

pdf("Primary risks.pdf", height=h, width = w)

# Transform the risks to percentages to align with the table.
point_estimates_overall$risk0 <- 100*point_estimates_overall$risk0
point_estimates_overall$risk1 <- 100*point_estimates_overall$risk1

ggplot(point_estimates_overall) +
  # Incidence bars for Nifedipine
  geom_bar(aes(y = outcome, x=risk1, fill = "Nifedipine"), stat = "identity",
           position = position_nudge(y = 0.2, x = 0.35), width = 0.4, alpha = 0.7) +
  geom_bar(aes(y = outcome, x=risk0, fill = "Labetalol"), stat = "identity",
           position = position_nudge(y = -0.2, x = 0.35), width = 0.4, alpha = 0.7) +
  scale_fill_manual(
    values = c(
      "Nifedipine" = "navy",
      "Labetalol" = "orange"
    )
  ) +
  labs(y = NULL, 
       x = "Risk (%)",
       fill = "Treatment Group", 
       ) +
  theme_minimal() +
  theme(text = element_text(color = "black"),
        legend.position = "bottom",
        axis.title.x.top = element_text(hjust = 0.8),
        axis.text.y = element_text(size = 12, color = "black"),
        axis.text.x = element_text(size = 12, color="black"),
        strip.text = element_text(size = 12),
        axis.title.x = element_text(size = 12, color = "black"),
        legend.text = element_text(size =12)#,
        #axis.title.x.bottom = element_text(hjust = 0.09)
        ) +
  theme(strip.placement = "outside") 

dev.off()

####


# Plot the Risk Differences

pdf("Primary risk differences.pdf", height=h, width = w)

# Transform the risk differences and CIs to per 100
point_estimates_overall$rd <- 100*point_estimates_overall$rd
point_estimates_overall$rd_lcl <- 100*point_estimates_overall$rd_lcl
point_estimates_overall$rd_ucl <- 100*point_estimates_overall$rd_ucl

ggplot(point_estimates_overall) +
  geom_point(aes(y = outcome, x = rd), size=3) +
  geom_errorbarh(
    aes(y = outcome, xmin = rd_lcl, xmax = rd_ucl),
    height = 0.2
  ) +
  geom_vline(xintercept = 0) +
  theme_minimal() +
  labs(
    y=NULL,
    x="Risk Difference (per 100)"
  ) +
  theme(text = element_text(color = "black"),
        legend.position = "bottom",
        axis.title.x.top = element_text(hjust = 0.8),
        axis.text.y = element_text(size = 12, color="black"),
        axis.text.x = element_text(size = 12, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"),
        strip.text = element_text(size = 12)#,
        #axis.title.x.bottom = element_text(hjust = 0.09)
  )

dev.off()


# Plot the Risk Ratios

pdf("Primary risk ratios.pdf", height=h, width = w)

ggplot(point_estimates_overall) +
  geom_point(aes(y = outcome, x = rr), size=3) +
  geom_errorbarh(
    aes(y = outcome, xmin = rr_lcl, xmax = rr_ucl),
    height = 0.2
  ) +
  geom_vline(xintercept = 1) +
  scale_x_log10(limits = c(NA, 2)) +
  theme_minimal() +
  labs(
    y=NULL,
    x="Risk Ratio"
  ) +
  theme(text = element_text(color = "black"),
        legend.position = "bottom",
        axis.title.x.top = element_text(hjust = 0.8),
        axis.text.y = element_text(size = 12, color="black"),
        axis.text.x = element_text(size = 12, color = "black"),
        axis.title.x = element_text(size = 12, color = "black"),
        strip.text = element_text(size = 12)#,
        #axis.title.x.bottom = element_text(hjust = 0.09)
  )

dev.off()



```